spinifex: An R Package for Creating a Manual Tour of Low-dimensional Projections of Multivariate Data

### 2019-06-28 paper/spyrison-cook.Rmd
/paper/ clean up for RJ resubmission.

keywords: exploratory data analysis, projection pursuit, high dimensional data, data visualization, statistical graphics, data science
preamble: >
  % preamble packages
link-citations: true
fig_caption: yes
toc: false
bibliography: spinifex_paper.bib
output: rticles::rjournal_article
  #bookdown::pdf_book:
   # base_format: rticles::rjournal_article #see sandbox for hard code solution.
---
\bibliography{spinifex_paper}
<!-- note that Di/Ursula have different setup and options and use static images.  -->
```{r setup_paper, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", 
  echo = TRUE, 
  collapse = TRUE,
  message = FALSE, 
  warning = FALSE, 
  error = FALSE,
  cache = FALSE, 
  cache.lazy = FALSE
)
library(spinifex)
library(ggplot2)
library(gridExtra)
library(dplyr)
```

>>>>

keywords: exploratory data analysis, projection pursuit, high dimensional data, data visualization, statistical graphics, data science
preamble: >
  % preamble packages
link-citations: true
fig_caption: yes
toc: false
bibliography: spyrison-cook.bib
output: rticles::rjournal_article
  #bookdown::pdf_book:
   # base_format: rticles::rjournal_article #see sandbox for hard code solution.
---
\bibliography{spinifex_paper}
<!-- tourrd3 example has different setup and options and uses static images.  -->
```{r setup_paper, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", 
  echo = TRUE, 
  collapse = TRUE,
  message = FALSE, 
  warning = FALSE, 
  error = FALSE,
  cache = TRUE, # needed for log and figure out?
  cache.lazy = FALSE
)
library(spinifex)
library(ggplot2)
library(gridExtra)
library(dplyr)
```

### 2019-06-28 paper/spyrison-cook.tex
/paper/ clean up for RJ resubmission.

{\centering \includegraphics[width=0.7\linewidth]{spinifex_paper_files/figure-latex/step0-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{spinifex_paper_files/figure-latex/step2-1}

@@

{\centering \includegraphics[width=1\linewidth]{spinifex_paper_files/figure-latex/step3-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spinifex_paper_files/figure-latex/step4-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spinifex_paper_files/figure-latex/JetClusterGood-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spinifex_paper_files/figure-latex/JetClusterBad-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spinifex_paper_files/figure-latex/DISclusterGood-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spinifex_paper_files/figure-latex/DISclusterBad-1}

@@

\bibliography{spinifex\_paper.bib}

>>>>

{\centering \includegraphics[width=0.7\linewidth]{spyrison-cook_files/figure-latex/step0-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{spyrison-cook_files/figure-latex/step2-1}

@@

{\centering \includegraphics[width=1\linewidth]{spyrison-cook_files/figure-latex/step3-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spyrison-cook_files/figure-latex/step4-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spyrison-cook_files/figure-latex/JetClusterGood-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spyrison-cook_files/figure-latex/JetClusterBad-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spyrison-cook_files/figure-latex/DISclusterGood-1}

@@

{\centering \includegraphics[width=5.83in,height=7in]{spyrison-cook_files/figure-latex/DISclusterBad-1}

@@

\bibliography{spyrison-cook.bib}
